---
title: "codebook for getting an cleaning data project"
author: "vincent trouillet"
date: "23/01/2018"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Original Datasets

The original datas are retrieve from this url : https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
A full description is available at the site where the data was obtained here:http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

### Overview

A group of 30 volunteers performed 6 different activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) while wearing a smartphone. Using its embedded accelerometer and gyroscope, The smartphone captured various data about their movements.

### Files containing in the zip

* _features.txt_: Names of the 561 features.
* _activity_labels.txt_: Names and IDs for each of the 6 activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING).
* _subject_train.txt_: A vector of 7352 integers, denoting the ID of the volunteer related to each of the observations in X_train.txt.
* _X_train.tx_t_: 7352 observations of the 561 features, for 21 of the 30 volunteers.
* _y_train.txt_: A vector of 7352 integers, denoting the ID of the activity related to each of the observations in X_train.txt.
* _subject_test.txt_: A vector of 2947 integers, denoting the ID of the volunteer related to each of the observations in X_test.txt.
* _X_test.txt_: 2947 observations of the 561 features, for 9 of the 30 volunteers.
* _y_test.txt_: A vector of 2947 integers, denoting the ID of the activity related to each of the observations in X_test.txt.

* _README.txt_ : General informations file
* _features_info.tx_ : More informations about the features.

 * all the files containing the raw datas and present in the Inertial Signals folders are not necessary for the present project and were not used.
 
### Retrieving the useful data
```{r, eval=FALSE}
X_train <- read.table("./UCI HAR Dataset/train/X_train.txt")
Y_train <- read.table("./UCI HAR Dataset/train/y_train.txt")
X_test <- read.table("./UCI HAR Dataset/test/X_test.txt")
Y_test <- read.table("./UCI HAR Dataset/test/y_test.txt")
Train_subject<-read.table("./UCI HAR Dataset/train/subject_train.txt")
Test_subject<-read.table("./UCI HAR Dataset/test/subject_test.txt")
```

example of one file containing the subjects id
```{r Subjects, echo=FALSE}
str(Test_subject)
```
example of one the file containing the activities id
```{r Activities, echo=FALSE}
str(Y_test)
```
sample of one file containing the features value
```{r FeatureValue, echo=FALSE}
X_test[1:5, 1:5]
```

## Merge training and test set to make one set of data

Bind the rows containing the subject (Train_subject,Test_subject)

Bind the rows containing the id of the activities related to the observations (Y_train,Y_test)

Bind the rows containing the features (X_train,X_test)

Finaly bind the column together 

```{r, eval=FALSE}
data_set<-cbind(rbind(Train_subject,Test_subject),rbind(Y_train,Y_test),rbind(X_train,X_test))
```
```{r merge, echo=FALSE}
data_set[1:5, 1:5]
```
After the merge the data set is made of 10299 obs. of 563 variables (subject, activity and features)

## Extracts only the measurements on the mean and standard deviation for each measurement.
```{r, eval=FALSE}
Feature <- read.table("./UCI HAR Dataset/features.txt", stringsAsFactors = FALSE)[,2]
```
```{r Feature, echo=FALSE}
str(Feature)
```

```{r, eval=FALSE}
feature_idx <- grep(("mean\\(\\)|std\\(\\)"), Feature)
Mean_Std_set <- data_set[, c(1, 2, feature_idx+2)]
colnames(Mean_Std_set) <- c("Subject", "Activity", Feature[feature_idx])
```

The resulting data Mean_Std_se is a data frame of 10299 obs  of 68 variables

## Uses descriptive activity names to name the activities in the data set

```{r, eval=FALSE}
Activity_names <- read.table("./UCI HAR Dataset/activity_labels.txt")
```

```{r Activity_names, echo=FALSE}
str(Feature)
```

```{r, eval=FALSE}
for (i in 1:6){
  Mean_Std_set$Activity[Mean_Std_set$Activity == i] <- as.character(Activity_names[i,2])
}
```

```{r meanstd, echo=FALSE}
Mean_Std_set[1:5, 1:5]
```

## Appropriately labels the data set with descriptive variable names
```{r, eval=FALSE}
names(Mean_Std_set) <- gsub("\\()", "", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("^t", "time", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("^f", "frequence", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("-mean", "Mean", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("-std", "Std", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("BodyBody", "Body", names(Mean_Std_set))
```

```{r label, echo=FALSE}
Mean_Std_set[1:5, 1:5]
```
##  From the data set in step 4, creates a second, independent tidy data set 
##    with the average of each variable for each activity and each subject
```{r, eval=FALSE}
library(dplyr)
Tidy_finalSet <- Mean_Std_set %>% group_by(Subject, Activity) %>% summarise_all(.funs = c(mean="mean"))
```

```{r tidyset, echo=FALSE}
Tidy_finalSet[1:5, 1:5]
```

```{r, eval=FALSE}
write.table(Tidy_finalSet, "./TidySet.txt", row.names = FALSE)
```
