---
title: "codebook for getting an cleaning data project"
author: "vincent trouillet"
date: "23/01/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Original Datasets

The original datas are retrieve from this url : https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
A full description is available at the site where the data was obtained here:http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones



```{r X_train, echo=FALSE}
str(X_train)
```

## 1) Merge training and test set to make one set of data
```{r, eval=FALSE}
data_set<-cbind(rbind(Train_subject,Test_subject),rbind(Y_train,Y_test),rbind(X_train,X_test))
```

After the merge the data (data_set) are made of 10299 obs. of 563 variables 

## 2) Extracts only the measurements on the mean and standard deviation for each measurement.
```{r, eval=FALSE}
Feature <- read.table("./UCI HAR Dataset/features.txt", stringsAsFactors = FALSE)[,2]
```
```{r Feature, echo=FALSE}
str(Feature)
```

```{r, eval=FALSE}
feature_idx <- grep(("mean\\(\\)|std\\(\\)"), Feature)
Mean_Std_set <- data_set[, c(1, 2, feature_idx+2)]
colnames(Mean_Std_set) <- c("Subject", "Activity", Feature[feature_idx])
```

The resulting data Mean_Std_se is a data frame of 10299 obs  of 68 variables

## 3)  Uses descriptive activity names to name the activities in the data set

```{r, eval=FALSE}
Activity_names <- read.table("./UCI HAR Dataset/activity_labels.txt")
```

```{r Activity_names, echo=FALSE}
str(Feature)
```

```{r, eval=FALSE}
for (i in 1:6){
  Mean_Std_set$Activity[Mean_Std_set$Activity == i] <- as.character(Activity_names[i,2])
}
```
## 4) appropriately labels the data set with descriptive variable names
```{r, eval=FALSE}
names(Mean_Std_set) <- gsub("\\()", "", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("^t", "time", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("^f", "frequence", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("-mean", "Mean", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("-std", "Std", names(Mean_Std_set))
names(Mean_Std_set) <- gsub("BodyBody", "Body", names(Mean_Std_set))
```
## 5) From the data set in step 4, creates a second, independent tidy data set 
##    with the average of each variable for each activity and each subject
```{r, eval=FALSE}
library(dplyr)
Tidy_finalSet <- Mean_Std_set %>% group_by(Subject, Activity) %>% summarise_all(.funs = c(mean="mean"))

write.table(Tidy_finalSet, "./TidySet.txt", row.names = FALSE)
```